
\addcontentsline{toc}{chapter}{Abstract}

\begin{abstract}
\mediumlinespacing
\hspace{10pt} A search for invisibly decaying Higgs bosons using proton-proton collision data collected by the CMS experiment at $\sqrt{s}=$~13~TeV is presented. For the first time, this search is performed using the complete dataset collected during the Run 2 phase of operation, corresponding to total integrated luminosity of 137.1~fb$^{-1}$. 

\hspace{10pt} In 2017 and 2018, to supplement the traditional trigger strategy based on the presence of missing transverse energy, a new dedicated trigger based on the Vector Boson Fusion jet topology was introduced. Its motivation, implementation and subsequent usage is described in detail. This addition further enhanced the sensitivity to the Vector Boson Fusion production mechanism by allowing for a new analysis category focused around previously inaccessible phase space.

\hspace{10pt} A combination with the study focusing on the 2016 data is performed. No deviations from the Standard Model have been observed and the final result is reported in the form of a 95~\% Confidence Level upper limit on the Br(H$\rightarrow$inv). The overall result of the measurement using the 2017 and 2018 data yields an observed (expected) Br(H$\rightarrow$inv)~$<$~15~\% (13~\%), while the full Run 2 limit stands at Br(H$\rightarrow$inv)~$<$~15~\% (12~\%). When interpreted in terms of dark matter searches, this result can be used to provide 90\% Confidence Level upper limits on the spin-independent dark matter-nucleon scattering cross section. Lastly, a study of projected sensitivity of this study for the conditions provided by the future upgrades of the CMS experiment is also presented. The projected limit for the total integrated luminosity of 3000~fb$^{-1}$ is placed, from the perspective of the CMS experiment, at Br(H$\rightarrow$inv)~$<$~3.8 \%, while a combined result from the ATLAS and CMS experiments is expected to yield Br(H$\rightarrow$inv)~$<~\text{2.5~\%}$.

\end{abstract}
